AP/PA Tables ITHIM Global

### 2023-09-15 injury_tables.Rmd
Added output version numbering - works on Latam branch
First version of results
Added csv outputs without version number

# read in table detailing the standardized modes
smodes <- read_csv('data/global/modes/standardized_modes.csv')

@@

```{r load_objects = "asis"}
output_version <- "v0.3"

@@

# write to csv
readr::write_csv(inj_counts_list, paste0('results/multi_city/inj/inj_counts_',output_version,'.csv')) # table containing all the fatality counts
```

@@

# output csv
readr::write_csv(rd,paste0( 'results/multi_city/inj/injury_risks_per_billion_kms_',output_version,'.csv'))
```

@@

# add active travel 
active_travel <- baseline_counts_pop %>% filter(mode == 'cycle' | mode == 'pedestrian')
active_travel <- active_travel %>% group_by(city, scenario, country, continent, measure ) %>% summarise(
                                   value = sum(value), model_population = sum(model_population), 
                                   mode ='active_travel')

@@

# write to csv
readr::write_csv(injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'), paste0('results/multi_city/inj/injury_risks_per_100k_pop_',output_version,'.csv'))
```

@@

# write to csv
readr::write_csv(true_distances_df, paste0('results/multi_city/inj/distances_',output_version,'.csv'))
```

@@

# write as csv
readr::write_csv(rd_hours, paste0('results/multi_city/inj/injury_risks_per_100million_h_',output_version,'.csv'))
```

>>>>

# read in table detailing the standardized modes
# smodes <- read_csv('data/global/modes/standardized_modes.csv')
smodes <- read_csv('results/multi_city/standardized_modes.csv')

@@

```{r load_objects = "asis"}
#output_version <- "v0.3"

@@

# write to csv with and without output version number
readr::write_csv(inj_counts_list, paste0('results/multi_city/inj/inj_counts_',output_version,'.csv')) # table containing all the fatality counts
readr::write_csv(inj_counts_list, paste0('results/multi_city/inj/inj_counts.csv'))
```

@@

# output csv with and without output version number
readr::write_csv(rd,paste0( 'results/multi_city/inj/injury_risks_per_billion_kms_',output_version,'.csv'))
readr::write_csv(rd,paste0( 'results/multi_city/inj/injury_risks_per_billion_kms.csv'))
```

@@

# add active travel 
active_travel <- baseline_counts_pop %>% filter(mode == 'cycle' | mode == 'pedestrian')
active_travel <- active_travel %>% group_by(city, scenario, country, continent, measure, model_population 
                                            ) %>% summarise(
                                   value = sum(value), 
                                   mode ='active_travel')

@@

# write to csv with and without output version number
readr::write_csv(injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'), paste0('results/multi_city/inj/injury_risks_per_100k_pop_',output_version,'.csv'))

readr::write_csv(injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'), paste0('results/multi_city/inj/injury_risks_per_100k_pop.csv'))
```

@@

# write to csv with and without output version number
readr::write_csv(true_distances_df, paste0('results/multi_city/inj/distances_',output_version,'.csv'))
readr::write_csv(true_distances_df, paste0('results/multi_city/inj/distances.csv'))
```

@@

# write as csv with and without output version number
readr::write_csv(rd_hours, paste0('results/multi_city/inj/injury_risks_per_100million_h_',output_version,'.csv'))
readr::write_csv(rd_hours, paste0('results/multi_city/inj/injury_risks_per_100million_h.csv'))
```

### 2023-09-15 summary_tables.Rmd
First version of results
Added csv outputs without version number

# Read trip_order
trip_order <- read_csv("data/global/trips/mode_order.csv")

@@

# Export ylls HB
write.csv(ylls,
            paste0('results/multi_city/health_impacts/ylls_',output_version,'.csv'),
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            paste0('results/multi_city/health_impacts/ylls_pathway_',output_version,'.csv'),
            row.names = F)
# Export deaths HB
write.csv(deaths,
            paste0('results/multi_city/health_impacts/deaths_',output_version,'.csv'),
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            paste0('results/multi_city/health_impacts/deaths_pathway_',output_version,'.csv'),
            row.names = F)

>>>>

# Read trip_order
# trip_order <- read_csv("data/global/trips/mode_order.csv")
trip_order <- read_csv("results/multi_city/mode_order.csv")

@@

# Export ylls HB

# write csv with output version number
write.csv(ylls,
            paste0('results/multi_city/health_impacts/ylls_',output_version,'.csv'),
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            paste0('results/multi_city/health_impacts/ylls_pathway_',output_version,'.csv'),
            row.names = F)
# Export deaths HB
write.csv(deaths,
            paste0('results/multi_city/health_impacts/deaths_',output_version,'.csv'),
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            paste0('results/multi_city/health_impacts/deaths_pathway_',output_version,'.csv'),
            row.names = F)

# write csv without output version number
write.csv(ylls,
            paste0('results/multi_city/health_impacts/ylls.csv'),
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            paste0('results/multi_city/health_impacts/ylls_pathway.csv'),
            row.names = F)
# Export deaths HB
write.csv(deaths,
            paste0('results/multi_city/health_impacts/deaths.csv'),
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            paste0('results/multi_city/health_impacts/deaths_pathway.csv'),
            row.names = F)

### 2023-09-15 summary_tables_PA_AP.Rmd
Added output version numbering - works on Latam branch
Added csv outputs without version number

###### Read in input parameters
output_version <- output_version

@@

# create csv file (summary_stats_Pm2.5_CO2 tab in Excel file above)
write_csv(bind_rows(l), paste0('results/multi_city/AP/desc_stats_', output_version ,".csv"))

>>>>

###### Read in input parameters
#output_version <-

@@

# create csv file (summary_stats_Pm2.5_CO2 tab in Excel file above) with and without output version number
write_csv(bind_rows(l), paste0('results/multi_city/AP/desc_stats_', output_version ,".csv"))
write_csv(bind_rows(l), paste0('results/multi_city/AP/desc_stats.csv'))
